The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-14 paper/conclusion.tex
add improvements to text

This study presented three simple models for the effects of binarity on 
occurrence rates measured by transit surveys.
The most realistic of these models (Model \#3) suggests that binarity does 
lead to underestimates in transit survey occurrence rates, but with less than 
$30\%$ relative error.
The model further suggests that hot Jupiter rates measured by transit surveys 
are biased to infer $\approx 1.3\times$ fewer hot Jupiters per star than 
surveys that only measure occurrence rates about single stars ({\it 
i.e..,} radial velocity surveys).
It also indicates that binarity's effects on the measured 
occurrence rates of Earth-sized planets are far smaller than current 
systematic uncertainties.
Though our models are simplistic, their agreement with Barclay \& 
Collaborator's recent detailed simulations indicate that they may capture the 
essential ingredients.

>>>>

This study presented three simple models for the effects of binarity on 
occurrence rates measured by transit surveys.
The simplest of these models (Model \#1) provides an order-of-magnitude 
estimate of how much binarity biases occurrence rates.
The most realistic of these models (Model \#3) suggests that binarity does 
lead to underestimates in transit survey occurrence rates, but with less than 
$30\%$ relative error.
The model further suggests that hot Jupiter rates measured by transit surveys 
are biased to infer $\approx 1.3\times$ fewer hot Jupiters per star than 
surveys that only measure occurrence rates about single stars ({\it 
i.e..,} radial velocity surveys).
It also indicates that binarity's effects on the measured 
rates of Earth-sized planets are far smaller than current 
systematic uncertainties.
Though our models are simplistic, their agreement with T. Barclay's recent 
independent simulations indicate that they capture the essential 
ingredients.

### 2017-11-14 paper/discussion.tex
paper: improved clarity; corrected eqn error
add improvements to text

\paragraph{How Has Binarity Been Considered in Occurrence Rate Measurements?}
Many authors have computed planet occurrence rates using transit 
survey data\footnote{
    An online list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
}.
Notable studies using {\it Kepler}\ data include those by Howard et al. 2012, 
Fressin et al., 2013, Foreman-Mackey et al., 2014, Dressing \& Charbonneau 
2015, and Burke et al. 2015.
Mostly if not entirely, these studies have ignored stellar multiplicity.
However, binarity clearly introduces a level of systematic uncertainty to 
pipeline completeness, as well as to star and planet counts.
No one has yet carefully studied the magnitude of this issue for 
{\it Kepler} occurrence rates.
While the present work does not resolve this problem, it suggests the 
approximate order of magnitude for the necessary correction factors.
%NOTE: the above might be better in a "discussion" section?

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have been undertaken to measure the multiplicity of 
almost all {\it Kepler}\ Objects of Interest 
(Howell et al. 2011; Adams et al. 2012, 2013; Horch et al. 2012, 2014; 
Lillo-Box et al. 2012, 2014; Dressing et al. 2014; Law et al. 2014; Cartier et 
al. 2015; Everett et al. 2015; Gilliland et al. 2015; Wang et al. 2015a, 
2015b; Baranec et al. 2016).
The results of these programs have been collected by Furlan et al. 
(2017), and they represent an important advance in understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's influence 
on the mass-radius diagram (Furlan \& Howell 2017).

%TODO: talk about N. R. Deacon et al 2015, Pan-STARRS1 here

To help clarify {\it Kepler}-derived occurrence rates, the high resolution 
imaging campaigns have not yet come full circle by observing a comparison 
sample of non-KOI host stars.
The most recent rate studies have thus used Furlan et al. (2017)'s 
catalog to test the effects of removing KOI hosts with known companions, which 
is an important step towards reducing contamination in the ``numerator'' of 
the occurrence rate (Fulton et al. 2017).
However, without an understanding of the multiplicity statistics of the 
non-KOI hosting stars that are assumed to be searchable, the 
true completeness, the true number of searchable stars, and thus the true 
occurrence rates will remain uncertain.

\paragraph{The Hot Jupiter Rate Discrepancy}
There is at least one context in which measurement of 
occurrence rates may already be showing the signatures of binarity.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
The discrepancy has weak statistical significance ($<3\sigma$).
That said, one reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by Gould et al. (2006), the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant planets (Santos et al 2004, Fischer and Valenti 2005).
The {\it Kepler}\ sample specifically has been measured to be more metal poor 
than the local neighborhood, with a mean metallicity of $[{\rm M/H}]_{\rm 
    mean}\approx -0.05$ (Dong et al., 2014; Guo et al., 2017).
Studying the problem in detail, Guo et al. recently argued that the 
metallicity difference could account for a $\approx 0.1\%$ difference in the 
measured rates between the CKS and {\it Kepler}\ samples~--~not a $\approx 
0.5\%$ difference.
Guo et al. concluded that ``other factors, such as binary contamination and 
imperfect stellar properties'' must also be at play.

Aside from surveying stars of varying metallicities, radial velocity and 
transit surveys differ in how they treat binarity.
Radial velocity surveys typically reject both visual and spectroscopic binaries
({\it e.g.}, Wright et al. 2012).
Transit surveys typically observe binaries, but the question of whether they 
were searchable to begin with is usually left for later interpretation.
In spectroscopic follow-up of candidate transiting planets, the prevalence of 
astrophysical false-positives may also lead to a bias against confirmation of 
transiting planets in binary systems.

Ignoring these complications, in this work we showed that
binarity does bias transit survey occurrence rates, simply through its 
effects on the number of searchable stars and the apparent radii of detected 
planets.
Specifically, our results from Sec.~\ref{sec:model_3} indicate that binarity 
might lead to underestimate HJ rates by a multiplicative factor of $\approx 
1.3$.

We assess the effect this might have towards resolving the hot Jupiter rate 
discrepancy by asking:
what is the probability of Wright et al. (2012)'s result, given a rate drawn 
from the stated bounds of Petigura et al. (in prep)? (See 
Table~\ref{tab:hj_rates}).
In other words, we first take the true HJ rate as $\Lambda_{\rm HJ} = 5.7 \pm 
1.3$, with Gaussian uncertainties, and then drawing from a Poisson 
distribution compute the probability of detecting at least 10 hot Jupiters in 
a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for Guo et al. 
(2017)'s measured metallicity difference between the {\it Kepler}\ field and 
the local solar neighborhood, 9\% of RV surveys would detect at least 10 hot 
Jupiters.
If we then multiply again by $1.3$ to account for binarity's bias, we find that
23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
would be quite teneous.
We emphasize that this result is only suggestive~--~a true resolution of the 
rate discrepancy would likely require a detailed understanding of the {\it 
Kepler}\ field's multiplicity statistics.

@@

Our models show that assuming a detected planet has equal probability of 
orbiting the primary or secondary leads to an overstatement of
binarity's population-level effects.
A planet orbiting the secondary does lead to extreme corrections, but these 
cases are rare outliers, because the searchable volume for secondaries is so 
much smaller than that for primaries.
Phrased in terms of the completeness, in our Model \#3 only $\sim 6\%$ of 
selected secondaries are searchable, compared to $\sim 60\%$ of selected 
primaries.
This means that when high-resolution imaging discovers a binary companion in 
system that hosts a detected transiting planet, the planet is much
more likely to orbit the primary.
This statement is independent of the fact that planets are often confirmed to 
orbit the primary by inferring the stellar density from the transit duration.

\paragraph{On the utility for future occurrence rate measurements}
Though they will be difficult to distinguish from false positives, {\it TESS}\ 
is expected to discover over $10^4$ giant planets (Sullivan et al. 2015).
One possible use of this overwhelmingly large sample will to measure an
occurrence rate of short-period giant planets.
Our work indicates that if this measurement is to be more precise than $\sim 
30\%$, binarity cannot be neglected.

\paragraph{What about {\it Kepler}?}
Barclay \& Collaborator (in preparation) have performed the exercise 
of taking stars selected by the {\it Kepler}\ team, pairing them with a 
population of secondaries, injecting a realistic distribution of planet radii, 
and then comparing the inferred occurrence rates with the true ones.
In their model, they find that binarity leads to an inferred rate of 
Earth-sized planets $\approx 10\%$ less than the true rate.
In our Model \#3, if all $\Lambda_i$'s are equal (a plausible assumption in 
the lack of evidence to the contrary), the underestimate is by 16\%.

>>>>

\paragraph{How has binarity been considered in occurrence rate measurements?}
Binarity introduces systematic uncertainty to star and planet counts, and also 
to estimates of pipeline completeness.
In spite of this fact, stellar multiplicity has mostly been ignored in 
calculations of planet occurrence rates using transit survey data\footnote{
    An online list of occurrence rate papers is maintained at 
    \url{https://exoplanetarchive.ipac.caltech.edu/docs/occurrence_rate_papers.html}
}~({\it 
e.g.}, Howard et al. 2012, Fressin et al., 2013, Foreman-Mackey et 
al., 2014, Dressing \& Charbonneau 2015, and Burke et al. 2015).
For {\it Kepler} occurrence rates specifically, it seems that no one has yet 
carefully assessed the magnitude of the issue.
While we do not resolve the problem, we do suggest
the approximate scale of the necessary corrections in a survey-independent 
manner.

Of course, on a system-by-system level stellar multiplicity affects the 
interpretation of planet candidates. High resolution imaging 
campaigns have measured the multiplicity of almost all {\it Kepler}\ Objects 
of Interest 
(Howell et al. 2011; Adams et al. 2012, 2013; Horch et al. 2012, 2014; 
Lillo-Box et al. 2012, 2014; Dressing et al. 2014; Law et al. 2014; Cartier et 
al. 2015; Everett et al. 2015; Gilliland et al. 2015; Wang et al. 2015a, 
2015b; Baranec et al. 2016).
The results of these programs have been collected by Furlan et al. 
(2017), and they represent an important advance in understanding the KOI 
sample's multiplicity statistics.
In particular, they can be immediately applied to rectify binarity's effects 
on the mass-radius diagram (Furlan \& Howell 2017).

The high resolution imaging campaign is also beginning to connect with
occurrence rate calculations.
The most recent rate studies have used Furlan et al. (2017)'s 
catalog to test the effects of removing KOI hosts with known companions, which 
helps reduce contamination in the ``numerator'' of 
the occurrence rate (Fulton et al. 2017, Petigura et al., in prep).
However, without an understanding of the multiplicity statistics of the 
non-KOI stars, the true completeness, and thus the true 
occurrence rates, will remain biased.
The first-order correction that we suggest, given the impracticality of 
performing high-resolution imaging of every selected star in a transit survey,
is to model the detection pipeline's efficiency while accounting for 
binarity.
%Simply put~--~do not assume binarity can be ignored, and take the relevant 
%systematic uncertainties about the selected stars into account.
For {\it Kepler}, this would require high resolution imaging of a
comparison sample of non-KOI host stars. If the associated multiplicity 
statistics are then included in a model of the pipeline's detection 
efficiency, and the number of selected stars is appropriately counted, it 
would correct most of binarity's biases.

\paragraph{The hot Jupiter rate discrepancy}
There is at least one context in which ignoring binarity may already be 
leading to discrepant measurements.
Hot Jupiter occurrence rates measured by transit surveys ($\approx 0.5\%$) are 
marginally lower than those found by radial velocity surveys ($\approx 1\%$; 
see Table~\ref{tab:hj_rates}).
The discrepancy has weak statistical significance ($<3\sigma$).
One reason to expect a difference is that the corresponding stellar 
populations have distinct metallicities.
As argued by Gould et al. (2006), the RV sample is biased towards 
metal-rich stars, which have been measured by RV surveys to preferentially 
host more giant planets (Santos et al 2004, Fischer and Valenti 2005).
The {\it Kepler}\ sample specifically has been measured to be more metal poor 
than the local neighborhood, with a mean metallicity of $[{\rm M/H}]_{\rm 
    mean}\approx -0.05$ (Dong et al., 2014; Guo et al., 2017).
Studying the problem in detail, Guo et al. recently argued that the 
metallicity difference could account for a $\approx 0.1\%$ difference in the 
measured rates between the CKS and {\it Kepler}\ samples~--~not a $\approx 
0.5\%$ difference.
Guo et al. concluded that ``other factors, such as binary contamination and 
imperfect stellar properties'' must also be at play.

Aside from surveying stars of varying metallicities, radial velocity and 
transit surveys differ in how they treat binarity.
Radial velocity surveys typically reject both visual and spectroscopic binaries
({\it e.g.}, Wright et al. 2012).
Transit surveys typically observe binaries, but the question of whether they 
were searchable to begin with is left for later interpretation.
In spectroscopic follow-up of candidate transiting planets, the prevalence of 
astrophysical false-positives may also lead to a bias against confirmation of 
transiting planets in binary systems.

Ignoring these complications, in this work we showed that
binarity biases transit survey occurrence rates through its effects on 
completeness, star counts, and the apparent radii of detected planets.
Specifically, our results from Sec.~\ref{sec:model_3} indicate that binarity 
could lead to underestimated HJ rates by a multiplicative factor of $\approx 
1.3$.

To assess the effect this might have towards resolving the hot Jupiter rate 
discrepancy we ask:
what is the probability of Wright et al. (2012)'s result, given a rate drawn 
from the stated bounds of Petigura et al. (in prep)? (See 
Table~\ref{tab:hj_rates}).
In other words, we first take the true HJ rate per thousand stars as 
$\Lambda_{\rm HJ} = 5.7 \pm 1.3$, with Gaussian uncertainties. 
We then draw from a Poisson distribution and compute the probability of 
detecting at least 10 hot Jupiters in a sample of 836 stars.
Without accounting for binarity or metallicity, only 4\% of RV surveys would 
detect at least 10 hot Jupiters.
If we multiply $\Lambda_{\rm HJ}$ by $1.2$ to account for Guo et al. 
(2017)'s measured metallicity difference between the {\it Kepler}\ field and 
the local solar neighborhood, 9\% of RV surveys would detect at least 10 hot 
Jupiters.
If we multiply once more by $1.3$ to account for binarity's bias, we find that
23\% of RV surveys would detect at least 10 hot Jupiters, and any discrepancy 
would be rather tenuous.
We emphasize that this result is only suggestive~--~a true resolution of the 
rate discrepancy would likely require a detailed understanding of the {\it 
Kepler}\ field's multiplicity statistics.

\paragraph{The rate of Earth analogs}
Per {\it Kepler}'s primary science objective, the rate of Earth-like planets 
orbiting Sun-like stars has been independently measured by Youdin, Petigura, 
Dong \& Zhu, Foreman-Mackey et al., and Burke et al. (2011, 2013, 2013, 2014, 
and 2015 respectively).
These efforts have found that the one-year terrestrial planet occurrence rate 
varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
assumptions that are made when retrieving the rate (Burke et al. 2015's 
Fig.~17).
In our Model \#3, the inferred rate is $\approx 0.84\times$ the true rate 
around single stars.
This bias is quite small compared to the other systematic factors that 
currently dominate the dispersion in $\eta_\oplus$ measurements.
If a future transit survey measures an absolute value of $\eta_\oplus$ to 
better than a factor of two, binarity might merit closer attention.

\paragraph{The CKS radius gap}
By improving the stellar radii... {\bf TODO}
%TODO DO THESE CALCULATIONS

@@

Our models show that assuming a detected planet has equal probability of 
orbiting the primary or secondary leads to an overstatement of
binarity's population-level effects.
A planet orbiting the secondary does lead to extreme corrections, but these 
cases are rare outliers, because the searchable volume for secondaries is so 
much smaller than that for primaries.
Phrased in terms of the completeness, in our Model \#3 only $\sim 6\%$ of 
selected secondaries are searchable, compared to $\sim 60\%$ of selected 
primaries.
This means that when high-resolution imaging discovers a binary companion in 
a system that hosts a detected transiting planet, the planet is much
more likely to orbit the primary.
This statement is independent of the fact that planets are often confirmed to 
orbit the primary by inferring the stellar density from the transit duration.

\paragraph{On the utility for future occurrence rate measurements}
{\it TESS}\ is expected to discover over $10^4$ giant planets (Sullivan 
et al. 2015).
Though they will be difficult to distinguish from false positives, one 
possible use of this overwhelmingly large sample will to measure an
occurrence rate of short-period giant planets.
Our work indicates that if this measurement is to be more accurate than $\sim 
30\%$, binarity cannot be neglected.

\paragraph{Independent approaches for estimating binarity's effects}
T. Barclay et al. (in prep) have performed the exercise of taking stars 
selected by the {\it Kepler}\ team, pairing them with a population of 
secondaries, injecting a realistic distribution of planet radii, 
and then comparing the inferred occurrence rates with the true ones.
In their model, they find that binarity leads to an inferred rate of 
Earth-sized planets $\approx 10\%$ less than the true rate.
In our Model \#3, if all $Z_i$'s are equal (a plausible assumption in 
the lack of evidence to the contrary), the underestimate is by a comparable 
16\%.

### 2017-11-14 paper/model_3.tex
add improvements to text

In this model, as in the previous one, all single and primary stars have 
identical properties.
Only the secondaries have masses, radii, and luminosities that vary between 
systems: $M\propto R \propto L^{1/\alpha}$.
The radii of planets are assigned independently of any host system
property, and are sampled from an intrinsic radius distribution, which we take 
as
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus \\
{\rm constant} & \text{for } r\leq2r_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
Following Howard et al. (2012)'s measurement, we take $\delta = -2.92$.
Our ``nominal model'' remains the same: the binary fraction is 0.44, 
$\alpha=3.5$, $\beta=\gamma=0$.
We take $Z_i$, the occurrence rate integrated over all planet radii for the 
$i^{\rm th}$ system type, to be equal for singles, primaries, 
and secondaries.

For this model, we forgo analytic development and focus only on numerics.
The occurrence rates are shown as a function of planet radius in 
Fig.~\ref{fig:errcases_model_3_log}.
For the assumed planetary and stellar distributions, the inferred rate is 
underestimated over all radii.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_3.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        Model 
        \#3.
        This model has fixed primaries and single stars, but varying 
        secondaries.
        The true planet radius distribution is a power law with exponent 
        $-2.92$ 
        above $2R_\oplus$, below which it is uniform (e.g., Howard et al., 
        2012).
    }
    \label{fig:errcases_model_3_log}
\end{figure}

\paragraph{Hot Jupiter Occurrence Rates}
Taking Fig.~\ref{fig:errcases_model_3_log} and counting the number of planets 
per star with $r>8r_\oplus$, we can compare the true and inferred hot Jupiter 
occurrence rates.
Under the above assumptions, the true rate is 9.1 hot Jupiters 
per thousand stars.
The inferred rate is 6.9 per thousand stars.
This means that the inferred rate underestimates the true rate by a 
multiplicative factor of $\sim\!1.3$.

However, this result only applies under the assumption that $Z_0 = 
Z_1 = Z_2$.
If hot Jupiters are less common around lower mass stars, it would be more 
sensible to consider $Z_2<Z_0$, while letting single stars and 
primaries host planets at the same rate.
Therefore in Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} we let 
$Z_2$ vary, and show the resulting inferred and true hot Jupiter 
($r>8r_\oplus$) rates.
The result is that the inferred rate is nearly independent of 
$Z_2$~--~this is because most ($<1/10$) secondaries are not searchable, 
and so their completeness fraction is much smaller than that of primaries or 
single stars.
This means far fewer detected hot Jupiters orbit secondaries, and so they 
hardly affect the inferred rate.
While the ``true rate'' across the entire population is linearly dependent on 
$Z_2$, the rate around 
singles and primaries (green line) is independent of that around secondaries.
Assuming that RV surveys are measuring the true rate around single stars (or 
primaries), this suggests that binarity might contributes to the 
HJ rate discrepancy at the $\sim 0.2\%$ level, independent of the HJ rate 
around secondaries.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/HJ_correction_inputrate_vs_HJratevalues.pdf}
    \caption{
        $X_i$ is the occurrence rate integrated over all possible phase 
        space for the $i^{\rm th}$ system type. $Z_2/Z_0=1$ 
        corresponds to an equal number of planets per secondary as per single 
        star;
        $Z_2/Z_0=0$ corresponds to secondaries not having any 
        planets.
        In our Model \#3, though the true HJ occurrence rate 
        is highly dependent on $Z_2$, 
        the inferred rate hardly depends on whether secondaries have HJs.
        This means that the ``correction factor'' between the inferred rate 
        and the true rate around single stars is underestimated by a 
        multiplicative 
        factor of $\approx1.3$, independent of the HJ rate around secondaries.
        The ``HJ rate'' is the summed rate from     
        Fig.~\ref{fig:errcases_model_3_log} above $8r_\oplus$.
    }
    \label{fig:HJ_correction_inputrate_vs_HJratevalues}
\end{figure}

\paragraph{The Rate of Earth Analogs}
The rate (density) of Earth-like planets orbiting Sun-like stars has 
been independently measured by Youdin, Petigura, Dong \& Zhu, 
Foreman-Mackey et al., and Burke et al., (2011, 2013, 2013, 2014, and 2015 
respectively).
These efforts have found that the one-year terrestrial planet occurrence rate 
varies between $\approx 0.03$ and $\approx 1$ per Sun-like star, depending on 
assumptions that are made when retrieving the rate (Burke et al. 2015's 
Fig.~17).

Our model does not explicitly include the rate density's period-dependence, 
because stellar binarity does not appreciably bias the period-dependence of 
occurrence rates measured by transit surveys\footnote{
    Note that stellar binarity does bias the {\it intrinsic} planet 
    occurrence as a function of planetary and binary periods. This is expected 
    from dynamical stability limits in $\geq$3 body systems, and has been 
    observationally confirmed (theory by Holman \& Wiegert 1999, and others 
    including Gongjie; confirmation from Wang et al 2014a, 2014b, Kraus et al 
    2014). 
    However our statement is that inferred rates as a function of planet     
    period should be negligibly affected by this, given the geometric bias 
    against long-period transit detections, and the fact that the period 
    distribution of solar-type binaries peaks at $\approx 100\,{\rm years}$ 
    (Raghavan et al 2010, Fig.~13).
}.
Instead, it allows us to evaluate the difference in the apparent and true rate 
as a function of radius 
(Fig.~\ref{fig:errcases_model_3_log}).
At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
true rate around single stars, assuming that the $Z_i$'s are equal.
Similar to the above case of the hot Jupiters, if we vary the true $Z_2$ 
while keeping $Z_0 = Z_1$, the ratio of the inferred to true rate 
around single stars hardly 
changes by only a few percent (shown in 
Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
The ratio of the inferred to the true rate, $(\Lambda_{\rm 
inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most $50\%$ 
in the (unrealistic) limiting case that secondaries do not host planets.

>>>>

As in the previous model, all single and primary stars in this model have 
identical properties.
The secondaries have masses, radii, and luminosities that vary between 
systems: $M\propto R \propto L^{1/\alpha}$.
The only addition is that we now let the radii of planets vary: they are 
assigned independently of any host system property, and are sampled from the 
true radius distribution, which we take as
\begin{align}
p_r(r)
&\propto
\left.
\begin{cases}
r^\delta & \text{for } r\geq 2r_\oplus \\
{\rm constant} & \text{for } r\leq2r_\oplus.
\end{cases}
\right.
\label{eq:model3_radius_distribution}
\end{align}
Following Howard et al. (2012)'s measurement, we take $\delta = -2.92$.
Our ``nominal model'' remains the same: the binary fraction is 0.44, 
$\alpha=3.5$, $\beta=\gamma=0$.
We take $Z_i$, the number of planets per single, primary, and secondary, to be 
equal.

For this model, we forgo analytic development and simply run our Monte Carlo 
program.
The resulting occurrence rates are shown in 
Fig.~\ref{fig:errcases_model_3_log}.
For the assumed planetary and stellar distributions, the inferred rate is 
underestimated over all radii.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_logs_model_3.pdf}
    \caption{
        Inferred planet occurrence rates as a function of planet radius in 
        Model 
        \#3.
        This model has fixed primaries and single stars, but varying 
        secondaries.
        The true planet radius distribution is a power law with exponent 
        $-2.92$ 
        above $2r_\oplus$, below which it is uniform ({\it e.g.}, Howard et 
        al., 
        2012).
    }
    \label{fig:errcases_model_3_log}
\end{figure}

\paragraph{Hot Jupiter occurrence rates}
Taking Fig.~\ref{fig:errcases_model_3_log} and counting the number of planets 
per star with $r>8r_\oplus$, we can compare the true and inferred hot Jupiter 
occurrence rates.
Under the above assumptions, the true rate is 9.1 hot Jupiters 
per thousand stars.
The inferred rate is 6.9 per thousand stars.
This means that the inferred rate underestimates the true rate by a 
multiplicative factor of $\sim\!1.3$.

However, this result only applies under the assumption that $Z_0 = 
Z_1 = Z_2$.
If hot Jupiters are less common around lower mass stars, it would be more 
sensible to consider $Z_2<Z_0$, while letting single stars and 
primaries host planets at the same rate.
Therefore in Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} we let 
$Z_2$ vary, and show the resulting inferred and true hot Jupiter 
($r>8r_\oplus$) rates.
The result is that the inferred rate is nearly independent of 
$Z_2$~--~this is because most ($<1/10$) secondaries are not searchable, 
and so their completeness fraction is much smaller than that of primaries or 
single stars.
This means far fewer detected hot Jupiters orbit secondaries, and so they 
hardly affect the inferred rate.
While the ``true rate'' across the entire population is linearly dependent on 
$Z_2$, the rate around 
singles and primaries (Fig.~\ref{fig:HJ_correction_inputrate_vs_HJratevalues} 
green line) is independent of that around secondaries.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=.6\textwidth]{figures/HJ_correction_inputrate_vs_HJratevalues.pdf}
    \caption{
        $Z_i$ is the occurrence rate integrated over all possible phase 
        space for the $i^{\rm th}$ system type. $Z_2/Z_0=1$ 
        corresponds to an equal number of planets per secondary as per single 
        star;
        $Z_2/Z_0=0$ corresponds to secondaries not having any 
        planets.
        In our Model \#3, though the true HJ occurrence rate 
        is highly dependent on $Z_2$, 
        the inferred rate hardly depends on whether secondaries have HJs.
        This means that the ``correction factor'' between the inferred rate 
        and the true rate around single stars is underestimated by a 
        multiplicative 
        factor of $\approx1.3$, independent of the HJ rate around secondaries.
        The ``HJ rate'' is the summed rate from     
        Fig.~\ref{fig:errcases_model_3_log} above $8r_\oplus$.
    }
    \label{fig:HJ_correction_inputrate_vs_HJratevalues}
\end{figure}

\paragraph{The rate of Earth analogs}
Our model does not explicitly include the rate density's period-dependence, 
because stellar binarity does not appreciably bias the period-dependence of 
occurrence rates measured by transit surveys\footnote{
    Note that stellar binarity does bias the {\it intrinsic} planet 
    occurrence as a function of planetary and binary periods. This is expected 
    from dynamical stability limits in $\geq$3 body systems, and has been 
    observationally confirmed (theory by Holman \& Wiegert 1999, and others 
    including Gongjie; confirmation from Wang et al 2014a, 2014b, Kraus et al 
    2014). 
    However our statement is that inferred rates as a function of planet     
    period should be negligibly affected by this, given the geometric bias 
    against long-period transit detections, and the fact that the period 
    distribution of solar-type binaries peaks at $\approx 100\,{\rm years}$ 
    (Raghavan et al 2010, Fig.~13).
}.
Instead, it allows us to evaluate the difference in the apparent and true rate 
as a function of radius 
(Fig.~\ref{fig:errcases_model_3_log}).
At Earth's radius, the result is that the inferred rate is $0.84\times$ the 
true rate around single stars, assuming that the $Z_i$'s are equal.
Similar to the above case of the hot Jupiters, if we vary the true $Z_2$ 
while keeping $Z_0 = Z_1$, the ratio of the inferred to true rate 
around single stars changes by only a few percent (shown in 
Fig.~\ref{fig:earth_inputrate_vs_etaearthratevalues}).
The ratio of the inferred to the true rate, $(\Lambda_{\rm 
inferred}/\Lambda)_{r=r_\oplus}$ varies substantially, but by at most $50\%$ 
in the (unrealistic) limiting case that secondaries do not host planets.
